Using spatially biased variables in ecosystem condition accounting with a GIS based workflow

### 2024-02-27 manuscript/HIAs.qmd
add EEA table

#EEA_tbl |>
#  kable()
# saveRDS(EEA_tbl, "../output/EEA-table.RDS")
```

>>>>

library(kableExtra)

# saveRDS(EEA_tbl, "../output/EEA-table.RDS")
```

```{r}
(EEA_tbl_out <- EEA_tbl |>
  ungroup() |>
  mutate(value = 
    paste0(
      format(median, 2), 
      " [",
      format(percentile_025,2),
      " - ",
      format(percentile_975,2),
      "] ")) |>
  rename(Indicator = indicator) |>
  select(
    -mean,
    -median,
    -percentile_025,
    -percentile_975,
    -Municipality
  )|>
  kbl(table.attr = "style = \"color: black;\"",
      align = "lr") |>
  kable_classic("striped",
    full_width = F) |>
  row_spec(0, bold=T) %>%
    pack_rows("Gran", 1, 3, 
      label_row_css = "background-color: #cef598; color: #000000;") |>
  pack_rows("Nord-Aurdal", 4, 6, 
      label_row_css = "background-color: #cef598; color: #000000;") |>
  pack_rows("Nordre Follo", 7, 9, 
      label_row_css = "background-color: #cef598; color: #000000;")
)
```
